---
title: <center> <h1>Survey Event Analysis Report</h1> </center>
author: <center> <h5>Jennie Eardley</h5> </center>
date: <center> <h5>06/06/2020</h5> </center>
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
livestream_data <- read_csv("data/synthesised_livestream.csv")
survey_data <- read_csv("data/clean_survey_data.csv")
location_data <- read_csv("data/location_distance_count.csv")
rating_data <- read_csv("data/rating_data.csv")
```

##### Analysis of the results of a survey about a sporting event which was held in Scotland. 

### Usual Residence of Attendees 

```{r, echo = FALSE, figures-side, fig.show = 'hold', out.width = "50%"}
# positioning graphs side by side 
survey_data %>% 
  select(residence) %>% 
  count(residence, sort = TRUE) %>% 
  ggplot() +
  geom_col(aes(x = residence, y = n), fill = "#008b8b") +
  labs(
    title = "Where Respondents Travelled From",
    x = "Residence",
    y = "Count"
  ) +
 theme_classic(base_size = 15) +
  theme(plot.title = element_text(hjust = 0.5))
local_authority_vector <- c("aberdeen", "aberdeenshire", "angus", "argyll and bute", "city of edinburgh", "comhairle nan eilean siar", "clackmannanshire", "dumfries and galloway", "dundee", "east ayrshire", "east dunbartonshire", "east lothian", "east renfrewshire", "falkirk", "fife", "glasgow", "highland", "inverclyde", "midlothian", "moray", "north ayrshire", "north lanarkshire", "orkney", "perth and kinross", "scottish borders", "shetland islands", "south ayrshire", "south lanarkshire", "stirling", "west dunbartonshire", "west lothian", "unknown")
local_authority_vector_rev <- rev(local_authority_vector)
survey_data %>% 
 filter(residence == "scotland") %>% 
  filter(local_authority != "unknown") %>% 
  count(local_authority, sort = TRUE) %>% 
    mutate(name = factor(local_authority, levels = local_authority_vector_rev)) %>%
  ggplot() +
  geom_col(aes(x = name, y = n), fill = "#008b8b") +
  coord_flip() +
  labs(title = "Respondents in Scotland by Local Authority",
       x = "Local Authority", y = "Count") +
  theme_classic(base_size = 15) +
   theme(plot.title = element_text(hjust = 0.5))
```

- Despite the event being held in Scotland, most of the respondents reported travelling from outwith Scotland. 
- The only further detail of locations in the data relates to Scottish local authorities. 
### The organisers are interested in reducing single car use are were interested in knowing about methods of travel both to and during the event
```{r, echo = FALSE, fig.show = 'hold', out.width = "50%"}
survey_data %>% 
  count(travel_method, sort = TRUE) %>% 
  filter(n >= 5) %>% 
  ggplot() +
  geom_col(aes(x = travel_method, y = n), fill = "#008b8b") +
  coord_flip() +
  labs(title = "Travel to Event",
       x = "Travel Method",
       y = "Count") +
  theme_classic(base_size = 15) +
  theme(plot.title = element_text(hjust = 0.5))
survey_data %>% 
  count(event_travel, sort = TRUE) %>% 
  filter(n >= 5) %>% 
  ggplot() +
  geom_col(aes(x = event_travel, y = n),fill = "#008b8b") +
  coord_flip() +
  labs(title = "Travel During Event",
       x = "Travel Method",
       y = "Count") +
  theme_classic(base_size = 15) +
  theme(plot.title = element_text(hjust = 0.5)) 
```

- The vast majority of respondents travelled to the event using their own vehicles
- The relatively remote location of the event may have prevented attendees from using public transport 

### Accommodation 

```{r, echo = FALSE, out.width = "75%", fig.align = "center"}
# splitting distances gained from the google map distance API into categories
hundred_and_over <- location_data %>% 
  arrange(desc(miles)) %>% 
  filter(miles >= 100) %>% 
  nrow()

ninety_to_hundred <- location_data %>% 
  arrange(desc(miles)) %>% 
  filter(miles >= 90 & miles < 100) %>% 
  nrow()

eighty_to_ninety <- location_data %>% 
  arrange(desc(miles)) %>% 
  filter(miles >= 80 & miles < 90) %>% 
  nrow()

seventy_to_eighty <- location_data %>% 
  arrange(desc(miles)) %>% 
  filter(miles >= 70 & miles < 80) %>% 
  nrow()

sixty_to_seventy <- location_data %>% 
  arrange(desc(miles)) %>% 
  filter(miles >= 60 & miles < 70) %>% 
  nrow()

fifty_to_sixty <- location_data %>% 
  arrange(desc(miles)) %>% 
  filter(miles >= 50 & miles < 60) %>% 
  nrow()

forty_to_fifty <- location_data %>% 
  arrange(desc(miles)) %>% 
  filter(miles >= 40 & miles < 50) %>% 
  nrow()

thirty_to_forty <- location_data %>% 
  arrange(desc(miles)) %>% 
  filter(miles >= 30 & miles < 40) %>% 
  nrow()

twenty_to_thirty <- location_data %>% 
  arrange(desc(miles)) %>% 
  filter(miles >= 20 & miles < 30) %>% 
  nrow()

ten_to_twenty <- location_data %>% 
  arrange(desc(miles)) %>% 
  filter(miles >= 10 & miles < 20) %>% 
  nrow()

under_ten <- location_data %>% 
  arrange(desc(miles)) %>% 
  filter(miles >= 1 & miles < 10) %>% 
  nrow()
# reversing factor levels as graph will be rotated
distance_levels <- rev(c("under ten", "ten to twenty", "twenty to thirty", "thirty to forty", "forty to fifty", "fifty to sixty", "sixty to seventy", "seventy to eighty", "eighty to ninety", "ninety to hundred", "hundred and over"))
location_distance_tibble <- tibble(under_ten, ten_to_twenty, twenty_to_thirty, thirty_to_forty, forty_to_fifty, fifty_to_sixty, sixty_to_seventy, seventy_to_eighty, eighty_to_ninety, ninety_to_hundred, hundred_and_over) %>% 
  pivot_longer(cols = (under_ten: hundred_and_over), 
               names_to = "number_that_stayed",
               values_to = "count") %>% 
 mutate_all(str_replace_all, "_", " ") %>%
  mutate(name = factor(number_that_stayed, (levels = distance_levels))) %>% 
  mutate(count = as.numeric(count)) %>% 
   ggplot() +
  geom_col(aes(x = name, y = count),fill = "#008b8b") +
  coord_flip() +
  theme_classic(base_size = 15) +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(
    title = "Driving Distance to Event",
    x = "Distance (miles)",
    y = "Count"
  ) 
location_distance_tibble
```

- Respondents stayed in 88 different cities, towns and villages in Scotland
- The most popular locations were: Comrie, Crieff and Perth
- 56% of respondents stayed in places with populations of under 500

```{r, echo = FALSE, out.width = "75%", fig.align = "center"}
survey_data %>% 
  count(accommodation_type, sort = TRUE) %>% 
  filter(n > 5) %>% 
  mutate(name = factor(accommodation_type, levels = c("self catering", "multiple", "hotel", "hostel", "guest house/b+b", "friends/relatives", "comrie", "camping/caravan", "at home"))) %>% 
ggplot() +
  geom_col(aes(x = name, y = n),fill = "#008b8b") +
 coord_flip() +
  labs(title = "Accommodation Types",
    x = "Accommodation Types",
      y = "Count") +
  theme_classic(base_size = 15) +
  theme(plot.title = element_text(hjust = 0.5)) 
  
```

- 49% of respondents stayed in self catering accommodation, they spent an average of £882 on accommodation
- 18% stayed at the event campsite - Comrie Croft, they spent an average of £194 on accommodation

### Digital Interaction with Event

The survey recorded different types of interaction with the livestream of the event. Respondents were asked to state if they had watched the livestream after the event, during the competition or during the races. Some respondents watched the livestream for two or more different categories. 
```{r, echo = FALSE, out.width = "75%", fig.align = "center"}
# sorting the livestream responses into categories depending on which type(s) of the livestream they interacted with
all_livestreams <- livestream_data %>% 
  filter(livestream_after_event == "1") %>% 
  filter(livestream_competition == "1") %>% 
  filter(livestream_races == "1") %>% 
  nrow()
after_event_and_competition <- livestream_data %>% 
  filter(livestream_after_event == "1") %>% 
  filter(livestream_competition == "1") %>% 
  filter(is.na(livestream_races)) %>% 
  nrow()
after_event_and_races <- livestream_data %>% 
  filter(livestream_after_event == "1") %>% 
  filter(livestream_races == "1") %>% 
  filter(is.na(livestream_competition)) %>% 
  nrow()
competition_and_races <- livestream_data %>% 
  filter(livestream_competition == "1") %>% 
  filter(livestream_races == "1") %>% 
  filter(is.na(livestream_after_event)) %>% 
  nrow()
races <- livestream_data %>% 
  filter(is.na(livestream_after_event)) %>% 
  filter(livestream_races == "1") %>% 
  filter(is.na(livestream_competition)) %>% 
  nrow()
after_event <- livestream_data %>% 
  filter(is.na(livestream_races)) %>% 
  filter(livestream_after_event == "1") %>% 
  filter(is.na(livestream_competition)) %>% 
  nrow()
competition <- livestream_data %>% 
  filter(is.na(livestream_after_event)) %>% 
  filter(livestream_competition == "1") %>% 
  filter(is.na(livestream_races)) %>% 
  nrow()

# graph showing the types of livestream watched 
livestream_tibble <- tibble(races, after_event, competition, competition_and_races, after_event_and_races, after_event_and_competition, all_livestreams) %>% 
  pivot_longer(cols = (races: all_livestreams), 
               names_to = "watched_livestream",
               values_to = "count") %>% 
  mutate_all(str_replace_all,"_", " ") %>%
  mutate(name = factor(watched_livestream, (levels = c("all livestreams", "competition and races", "after event and races", "after event and competition", "races", "competition", "after event")))) %>% 
  mutate(count = as.numeric(count)) %>% 
   ggplot() +
  geom_col(aes(x = name, y = count),fill = "#008b8b") +
  coord_flip() +
  theme_classic(base_size = 15) +
  theme(plot.title = element_text(hjust = 0.5)) +
  labs(
    title = "Type of Livestream Watched",
    x = "Type of Livestream",
    y = "Count"
  ) 
livestream_tibble
```

- Most people only watched one type of livestream
- In the free text comments, unreliable wifi was frequently mentioned and some respondents stated that this prevented them from watching the livestream during the event

```{r}
rating_data %>% 
   mutate(name = factor(rating, levels = c("excellent", "good", "average", "poor", "very poor"))) %>% 
  ggplot() +
  geom_bar(aes(x = name, fill = media_type), position = "dodge") +
  scale_fill_manual(values = c("#004c4c", "#008080", "#66b2b2", "#b2d8d8"), name = "Media Type", 
                                        labels = c("Facebook and Twitter",
                                                    "Printed Programme", 
                                                    "Social Programme",
                                                    "Website Info")) +
  theme_classic(base_size = 15) +
   theme(plot.title = element_text(hjust = 0.5)) +
  labs(title = "Satisfaction Levels", 
       x = "Rating", 
       y = "Count") 
```

- 34% of respondents followed the event on Twitter and/or Facebook
- 85% of those who engaged rated the quality as excellent or good 

### Actionable Points

- Consider alternative transport options 
- Investigate increasing the availability of water
- Review wifi availability 
- Consider accessibility of public transport to social events 


### Recommendations for Future Surveys

- Ask for more specific areas in other UK, if there are particularly popular areas, promoting shared transport in these areas could be promoted
- Supply more options for the respondents to select from drop down lists to allow for more efficient categorisation
- Ask about Twitter and Facebook separately to allow for analysis of popularity of different social media approaches
- Ask for ratings by day of event to enable the organisers to know which type of events are the most popular

